A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-06 paper.tex
Evaluate for performance between MAM and E2EE

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{float}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\graphicspath{{./images/}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

% alternative solution => IPFS(data) + MAM(index)
\subsection{Digital Identity}
The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. In our architecture, a self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority. TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable. The identity information such as public key, unique identifiers of services and metadata consists a DID document. One can easily prove himself by sharing the identifier on MAM without any authority.

Through TangleID, containing public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel. The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner. During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible. See Fig.~\ref{fig:TangleID}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

@@

\section{Decentralized Data Marketplace Case Study}
Trading Models of Decentralized Data Marketplace
\subsubsection{Set Up}
All participants need to register on TangleID\cite{TangleID}, a self-sovereign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.

\subsubsection{Launch Data Products}
To launch a data product, data providers need to create a MAM channel/endpoint and a Product Contract. However, considering IoT devices have no ability to handle both uploading data to MAM and interacting Ethereum smart contracts while collecting continuous data with low computing power, these works are offloaded to brokers.

The details of data product, such as data price, MAM channel/endpoint ID and time period are listed on the Product Contract. As regard to the encryption key of data product, it is certified by a broker with blind signature\cite{blindSig}, a mechanism that allows users to sign contents without knowing it, and written the signed key on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product}.

Data providers start uploading data once the MAM channel/endpoint are created, each MAM message contains encrypted contexts along with signatures which allows data consumers to check the integrity. In addition, one can perform the signature validation without the encryption key on MAM.

@@

\subsubsection{Trading}
Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the "access" of data products on MAM instead of the files to consumers. The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can retrieve it from Product Contract.

Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants. Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process. The key sending process is shown in Fig.~\ref{fig:key_exchange}.

@@

\subsubsection{Refunding}
Subscribing to future data is a high-risk which data provider may not upload data as the agreement set after receiving the subscription fee. Therefore, in our proposed architecture, data consumers can initiate a refund procedure if the data is not available or defective. The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM. When the refund procedure is launched, all consumers start voting based on their opinions on the data product. Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{mam_create}
    \caption{Time cost of MAM creation.}
    \label{fig:mam_create}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{mam_send}
    \caption{Time cost of sending a message through MAM.}
    \label{fig:mam_send}
\end{figure}

@@

>>>>

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{float}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic,algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\graphicspath{{./images/}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\subsection{Digital Identity}
The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.

\begin{table}[h]
	\caption{The comparism of centralized and decentralized identity model}
	\label{tab:did}
	\begin{tabularx}{\linewidth}{|l|X|X|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\
		\hline
		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
		\hline
		Protability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
		\hline
	\end{tabularx}
\end{table}

Centralized identity model may have single point failure in identifier management and security issues like data leakage. With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged. Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.

In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata. The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments. If a VC is verified via issuer's public key, the message will be labelled as trusted. Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.

\begin{figure}[h]
    \centering
    \includegraphics[width=3.in]{DID_VC}
    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
    \label{fig:did_vc}
\end{figure}

In our architecture, a decentralized identity system TangleID\cite{TangleID} is used, which is built on top of MAM where change logs of DIDs are traceable. One can easily prove himself by sharing the identifier on MAM without any authority.

Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel. The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner. During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible. See Fig.~\ref{fig:TangleID}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

@@

\section{Decentralized Subscription-based Data Trading Case Study}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.

\subsection{Prerequisite}
All participants are required to register on TangleID to get DID document and public/private key pair for sensitive contents exchange and authentication. An Ethereum account is also needed to interact with smart contracts and transfer Ethereum tokens.

\subsection{Launch Data Products}
To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract. For those resource-constraint IoT devices, the MAM related operations can be delegated to Tangle-accelerator, as mentioned in Section.~\ref{section:ta_endpoint}. And brokers are responsible for Product Contract creation.

The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract. As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}. Finally, the data product is launched and data providers can start uploading data.

@@

\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
    function addHashedKey(
        string memory _hashedKey
    ) public {
        require(
            msg.sender == provider,
            "Only provider can add hashed key."
        );
        require(
            state == State.Launched,
            "One key has been certified."
        );
        hashedKey = hashedKey;
        emit newHashedKey(hashedKey);
    }

    function addCertifiedKey(
        string memory _certifiedKey
    ) public {
        require(
            msg.sender == broker,
            "Only broker can add certifiedKey."
        );
        require(
            state == State.Launched,
            "One key has been certified."
        );
        certifiedKey = _certifiedKey;
        state = State.KeyCertified;
        emit newCertifiedKey(certifiedKey);
    }
\end{lstlisting}

\subsection{Trading}
Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers. The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it via Product Contract.

Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to public. Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process. The key sending process is shown in Fig.~\ref{fig:key_exchange} and Listing.~\ref{lst:key_exchange}. The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.

@@

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4,
	basicstyle=\scriptsize
}
\lstset{style=solidity}

\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
    function addEncryptKey(
        address _consumer,
        string memory _encryptKey
    ) public {
        require(
            msg.sender == provider,
            "Only provider can add the encrypted key."
        );
        require(
            consumer2Purchase[_consumer].isKeyAdded == false,
            "Encryption key has been added."
        );
        consumer2Purchase[_consumer].encryptKey = _encryptKey;
        consumer2Purchase[_consumer].isKeyAdded = true;
        emit newEncryptKey(_consumer, _encryptKey);
    }
\end{lstlisting}

\subsection{Unsubscribe to Data Products}
Data consumers can unsubscribe to data products when they're not interested anymore. Product Contract hold an unsubscriber list to record the unsubscribers. When data consumers trigger the unsubscribe event, a withdraw function is executed to pay subscription fee to providers and return the rest of the fee back to consumers. The amount of payment distributed to different players is defined in formula~\ref{equation:unsubscribe_provider}, \ref{equation:unsubscribe_broker}, \ref{equation:unsubscribe_consumer}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, $N$ is the number of consumers in this contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription.

In SaaS, the cancellation fee is a way to make sure the service providers are protected. It is commonly used in pre-paid subscription-based services that allows service providers charge cancellation fee if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue that should be carefully studied.

Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data. The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract. Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.

\begin{equation}
\label{equation:unsubscribe_provider}
    F_{DataProvider}(i) = price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} 
\end{equation}

\begin{equation}
\label{equation:unsubscribe_broker}
    F_{Broker}(i) = price \frac{i-1}{M} F_{b} -F_{t}
\end{equation}

\begin{equation}
\label{equation:unsubscribe_consumer}
    F_{Consumer}(i) = price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t}
\end{equation}

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{unsubscribe}
    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively. Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
    \label{fig:unsubscribe}
\end{figure}

\subsection{Launch a Refund}
Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee. Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective. When the refund procedure is launched, all consumers vote to decide whether the refund is established. See Fig.~\ref{fig:refund}. Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following:

\begin{equation}
    F_{DataProvider}(i) = Nprice \frac{i-1}{M} (1-F_{b}) -F_{t}
\end{equation}

\begin{equation}
    F_{Broker}(i) = Nprice \frac{i-1}{M} F_{b} -F_{t}
\end{equation}

\begin{equation}
    F_{Consumer}(i) = price (1-\frac{i-1}{M}) -F_{t}
\end{equation}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.5in]{refund}
    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers. Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
    \label{fig:refund}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{mam_create}
    \caption{Elapsed time of MAM creation.}
    \label{fig:mam_create}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{mam_send}
    \caption{Elapsed time of sending a message through MAM.}
    \label{fig:mam_send}
\end{figure}

@@

\subsection{Smart Contract}
In this experiment, we investigate the cost of executing Product Contract with Ethereum web browser based IDE Remix that we can define the minimum cost, which data providers should pay in order to launch a product and processing a trade.  On top of this evaluation, data providers can consider how to set the price to eventually generate profits. The estimated cost is in Ether, which is 238 USD at the time of writing, yet the price is dynamic from time to time. To conquer this condition, the authors in \cite{MindMyValue} suggested to analyze with a fixed range of Gas price,  yet the main drawback of low Gas price is the increase of time required before a transaction is validated. According to the report of Ethereum network\cite{ethereumChart} in 2020 (January to June), we set this range from 7.3 Gwei to 26.5 Gwei, which is $7.3 \times 10^{-9}$ and $2.65 \times 10^{-8}$ Ether respectively, the minimum average and average gas price. The Gas usage estimation is shown in Table.~\ref{tab:gas}.

\begin{table*}[h]
	\caption{Gas consumption for each function of Product Contract}
	\label{tab:gas}
	\centering
	\resizebox{0.7\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
		\hline
		generate contract & Broker & 2251002 \\
		subscribe product & Consumer & 44486 \\
		upload signed key to consumer & Provider & 147369 \\
		upload certified key & Broker & 167678 \\
		upload hased encryption key & Provider & 166784 \\
		update the amount of uploaded data & Broker & 32825 \\
		request refund & Consumer & 22545 \\
		unsubscribe & Consumer & 22641 \\
		withdraw & Broker/Provider/Consumer & 14719 \\
		\hline
	\end{tabular}
	}
\end{table*}

Note that data uploading is only related to MAM operations on IOTA, which does not require any fees. Therefore, the Gas estimation only includes trading processes. Creating a Product Contract (Listing \ref{lst:constructor}) costs the most Gas (0.164 - 0.596 Ether), providers should have enough Ethers to launch the product at start. Functions (Listing \ref{lst:key_exchange} (0.012 - 0.044 Ether) and Listing \ref{lst:key_certification}) (0.022 - 0.0834 Ether) that are related to key certification and key exchange need a lot of gas as well. Storage on blockchain is expensive. For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero according to Ethereum Yellow Paper\cite{Ethereum}. However, in our trading model, we preserve a lot of information in Product Contract in order to record as more details as possible during trading procedures, such as ciphertexts,  signatures during key certification and key exchange. Especially, in the key exchange protocol, it takes several steps of communications between brokers, data providers and data consumers via storing states to Product Contract. Therefore, it is worth to explore the usage of the non-interactive zero-knowledge protocol such as zk-SNARKS(zero-knowledge succinct non-interactive argument of knowledge)\cite{Snark} which can generate proofs off-chain and simplify the verification process that could not only reduce network and storage cost but also improve the privacy and security of encryption keys. However, using zero-knowledge protocol is out of the scope of this paper.

Base on Gas estimation in Table.~\ref{tab:gas}, we calculate the exact Ether with Formula~\ref{equa:ether_calculation} that data providers and data consumers need during the trade in Table.~\ref{tab:ether}. We combine the Gas usage of providers and brokers, since the brokerage fee is also a critical cost to sustain the trade, which providers should considered. We conclude the four situations during the trading process: w/o refund and unsubscribe, w/ refund only, w/unsubscribe and w/ refund and unsubscribe. The condition of w/o refund and unsubscribe represents the basic cost of  triggering regular functions, such as launch, add encryption key.

\begin{equation}
\label{equa:ether_calculation}
Ethers = Gas \ Price \times Gas \ Amount
\end{equation}

When a consumer request a refund, he/she need to pay 0.001 Ether additionally. Then if the refund established, all participants will withdraw the payment, which is already included in the basic cost. Observing the situation of w/ unsubscribe and w/ refund and unsubscribe, it does not cost them much more Ether for consumers. However, the data provider need to update all encryption keys for remaining consumers that \textit{update encrypt key} will be triggered $N$ times, where $N$ is the amount of remaining subscribers. This would cost data providers a lot if the unsubscription is frequent or many consumers subscribe to the data product. Hence, an efficient, low-cost and secure way to perform access control while recording the unsubscription process transparent is important. An alternative strategey coming up with the latest development of MAM, which is renaming to Streams\cite{stream}, provides a new functionality for subscribers to unsubscribe to data streams, thus, it is possible to perform access control directly through it rather than uploading new encryption key to the Product Contract. Nevertheless, Streams is still in an alpha version, the details and protocol still need to be well studied.

\begin{table*}[h]
	\caption{Data Price Estimation}
	\label{tab:ether}
	\centering
	\resizebox{0.8\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{condition} & \textbf{sender} & \textbf{minimum price (Ether)} & \textbf{maximum price (Ether)} \\
		\hline
		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.224 & 0.816 \\
		 & consumer & 0.003 & 0.011 \\
		\hline
		\multirow{2}{*}{w/ refund} & provider & 0.224 & 0.816 \\
		 & consumer & 0.004 & 0.016 \\
		\hline
		\multirow{2}{*}{w/ unsubscribe} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
		 & consumer & 0.004 & 0.016 \\
		\hline
		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & \makecell{0.224 + 0.011N \\ (update encryption key for consumers)} & \makecell{0.816  + 0.011N \\ (update encryption key for consumers)}\\
		 & consumer & 0.005 & 0.020 \\
		\hline
	\end{tabular}
	}
\end{table*}
\subsection{MAM vs. the delegated MAM}
What follows is an account of performance comparison between MAM and delegated MAM (E2EE) for different payload sizes. Elapsed time for internet communication and PoW are not included, because the following processes starting from sending message to tangle-accelerator are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too. The two excluded steps take much more time than encrypting messages only, so counting these two steps would cause extreme values.

The steps counted in MAM benchmark including:
\begin{itemize}
	\item Encrypt input payload
	\item Publish final message on IOTA Tangle
\end{itemize}

The steps counted in E2EE benchmark including:
\begin{itemize}
	\item Generate symmetric key for encryption
	\item Hash input payload
	\item Encrypt input payload
	\item Transmit final message to tangle-accelerator
\end{itemize}

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{mam_vs_e2ee}
    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
    \label{fig:mam_vs_e2ee}
\end{figure}

On Fig.~\ref{fig:mam_vs_e2ee}, a comparison of the two result reveals elapsing time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for low-level embedded system to send authenticated streaming data. Next, regarding the trend of the two lines, the performance of E2EE is obviously more steady than MAM in the given range. The bump of MAM performance around 750 bytes proves this point. Moreover, the performance of E2EE is almost under constant time, but MAM takes linear time on encrypting messages.
